### 2017-12-01 manuscript.rmd
removed vrange_simmap making

```{r simmap_making, echo=F, message=F, warning=F, include=F}
#Stochastic trait mapping:
#Make simmap objects
#print("SIMMAP Sex Distribution")
make.simmap(ultratree, sex, nsim = 100, message=FALSE) -> sex_sim
#print("SIMMAP Palpons")
make.simmap(ultratree, palpons, nsim = 100, message=FALSE) -> palpons_sim
#print("SIMMAP Tentilla")
make.simmap(ultratree, tentilla, nsim = 100, message=FALSE) -> tentilla_sim
#print("SIMMAP Tentilla2")
make.simmap(ultratree, tentilla2, nsim = 100, message=FALSE) -> tentilla_sim2
#print("SIMMAP Nectosome")
make.simmap(ultratree, nectosome, nsim = 100, message=FALSE) -> nectosome_sim
#print("SIMMAP Nectosome Position")
make.simmap(ultratree, necto_pos, nsim = 100, message=FALSE) -> necto_pos_sim
#print("SIMMAP Nectophore Types")
make.simmap(ultratree, necto_types, nsim = 100, message=FALSE) -> necto_types_sim
#print("SIMMAP Bracts")
make.simmap(ultratree, bracts, nsim = 100) -> bracts_sim
#print("SIMMAP Habitat")
make.simmap(ultratree, vrange, nsim = 100, message=FALSE) -> vrange_sim

>>>>

```{r simmap_making, echo=F, message=F, warning=F, include=F}
#Stochastic trait mapping:
#Make simmap objects
#print("SIMMAP Sex Distribution")
make.simmap(ultratree, sex, nsim = 100, message=FALSE) -> sex_sim
#print("SIMMAP Palpons")
make.simmap(ultratree, palpons, nsim = 100, message=FALSE) -> palpons_sim
#print("SIMMAP Tentilla")
make.simmap(ultratree, tentilla, nsim = 100, message=FALSE) -> tentilla_sim
#print("SIMMAP Tentilla2")
make.simmap(ultratree, tentilla2, nsim = 100, message=FALSE) -> tentilla_sim2
#print("SIMMAP Nectosome")
make.simmap(ultratree, nectosome, nsim = 100, message=FALSE) -> nectosome_sim
#print("SIMMAP Nectosome Position")
make.simmap(ultratree, necto_pos, nsim = 100, message=FALSE) -> necto_pos_sim
#print("SIMMAP Nectophore Types")
make.simmap(ultratree, necto_types, nsim = 100, message=FALSE) -> necto_types_sim
#print("SIMMAP Bracts")
make.simmap(ultratree, bracts, nsim = 100) -> bracts_sim
#print("SIMMAP Habitat")
```
